A holomorphic approach to membranes and fivebranes

### 2022-07-21 fivebranes/kr.tex
small error
merge

The first ingredient in determining an explicit formula for Verma modules is a direct calculation.
\begin{lem}
\label{lem:R}
The explicit formula for $R = R(t,t_1,t_2,r)$ is
%\beqn
%R = \frac{1}{(1-t_1^{-1} q)(1-t_1t_2^{-1}q)(1-t_2 q)}\prod_{a=+1,-1}(1-t_1^{-1} q^{1/2} r^a)(1-t_1 t_2^{-1} q^{1/2} r^a)(1-t_2 q^{1/2} r^a)
%\eeqn
\beqn
R = \frac{1}{(1-t_1^{-1} q)(1-t_1t_2^{-1}q)(1-t_2 q)}\prod_{a=+1,-1}(1-t_1^{-1} q^{1/2} r^a)(1-t_1 t_2^{-1} q^{1/2} r^a)(1-t_2 q^{1/2} r^a)
\eeqn
\end{lem}

@@

\parsec[s:unrefinedA]

In this section we deduce an explicit formula for the character of the type $A$ modules $I_A(\lambda_1,\lambda_3)$ after specializing $t_1=t_2=1$.

\begin{prop}
\label{prop:chA}
Let $\lambda_1,\lambda_3 \geq 0$. 
The $t_1=t_2=1$ specialization of $\ch \, \til I_A(\lambda_1,\lambda_3)$ is given by the expression
\beqn
\frac{t^{2\lambda_1-3 \lambda_3+6}}{(1-t^2)^3(1-r^{-2})} \left(r^{\lambda_3} p_{\lambda_1}(t^{-1}r) (1-t^{-1}r^{-1})^3 - r^{-\lambda_3-2} p_{\lambda_1}(t^{-1}r^{-1})(1-t^{-1}r)^3 \right) 
\eeqn
where $p_{\lambda_1}(x) = \frac12 \left(\lambda_1^2 x^2 + \lambda_1 x^2 - 2\lambda_1^2x -4 \lambda_1 x + \lambda_1^2 + 3\lambda_1 +2\right)$. 
\end{prop}

\begin{proof}
In this specialization we just see the dimension of the highest weight $SU(3)$ representations
\[
\ch_{SU(3)}^{\lambda_1+j}(t_1=t_2=1) = \frac{(\lambda_1+j+1)(\lambda_1+j+2)}{2} .
\]

We thus arrive at the expression for the $j$th term in the sum appearing in equation \eqref{eqn:chA2}:
\beqn\label{eqn:MA2}
\ch \til M_A(\lambda_1+j,\lambda_3+j)_{t_1=t_2=1} = R(t,r) t^{2 \lambda_1-3\lambda_3-j} \frac{(\lambda_1+j+1)(\lambda_1+j+2)}{2} \frac{r^{\lambda_3+j}-r^{-\lambda_3-j-2}}{1-r^{-2}} 
\eeqn
where $R(t,r)$ is the specialization at $t_1=t_2=1$ of $R$ from Lemma \ref{lem:R}:
\[
R(t,r) = R|_{t_1=t_2=1} = \frac{(1-tr)^3 (1-t r^{-1})^3}{(1-t^2)^3} .
\]
In equation \eqref{eqn:MA2} we have also utilized the $SU(2)$ character formula for the irreducible module of heighest weight $\lambda_3+j$. 
%\[
%r^{\lambda_3+j}+ r^{\lambda_3+j-2} + \cdots + r^{-\lambda_3-j} = \frac{r^{\lambda_3+j}-r^{-\lambda_3-j-2}}{1-r^{-2}} ,
%\]

Now, observe the formal identity 
\[
\sum_{j \geq 0} \frac{(\lambda_1+j+1)(\lambda_1+j+2)}{2} x^j = \frac{p_{\lambda_1}(x)}{(1-x)^3}  
\]
where $p_{\lambda_1}(x)$ is as in the statement of the proposition.
Using this identity, we evaluate
\begin{align*}
\ch \til I_A(\lambda_1,\lambda_3)|_{t_1=t_2=1} & = \frac{R(r,t) t^{2 \lambda_1-3 \lambda_3}}{1-r^{-2}} \left(\frac{r^{\lambda_3} p_{\lambda_1}(t^{-1}r)}{(1-t^{-1}r)^3} - \frac{r^{-\lambda_3-2}p_{\lambda_1}(t^{-1}r^{-1})}{(1-t^{-1}r^{-1})^3} \right) \\ 
& = \frac{t^{2\lambda_1-3 \lambda_3+6}}{(1-t^2)^3(1-r^{-2})} \left(r^{\lambda_3} p_{\lambda_1}(t^{-1}r) (1-t^{-1}r^{-1})^3 - r^{-\lambda_3-2} p_{\lambda_1}(t^{-1}r^{-1})(1-t^{-1}r)^3 \right) .
\end{align*}
This completes the proof
\end{proof}

In the case that $\lambda_1=0$ and $\lambda_3=1$ we see that this specialized character simplifies to
\beqn
\ch \til I_A(0,1)|_{t_1=t_2=1} = \frac{t^3(r+r^{-1}) + 1 - 3 t^2}{(1-t^2)^3} .
\eeqn

In the case that $\lambda_1 = 1$ and $\lambda_3 = 0$ we see that this unrefined character simplifies to
\beqn
 \ch \til I_A(1,0)|_{t_1=t_2=1} = \frac{t^6(r^2 + r^{-2} + 1) - 3 t^7 (r + r^{-1}) + 3t^8 }{(1-t^2)^3} .
\eeqn

Finally, for general $\lambda_1,\lambda_3$ we specialize further $t=r$ and substitute $q = t^2$ to obtain
\beqn
\ch \til I_A(\lambda_1,\lambda_3) = \frac{t^{2 \lambda_1 - 2 \lambda_3 + 2}}{1 - t^2} = \frac{q^{\lambda_1-\lambda_3+1}}{1-q} .
\eeqn

@@

We now turn to the formula for the totally unrefined character of $\til I_A(\lambda_1,\lambda_3)$, before specializing $t_1=t_2=1$.
The character will be given in terms of a generating function for highest weight $SU(3)$ representations.

Our first aim is to deduce a closed formula for the following generating function
\beqn
\til p^{\lambda_1} (x,t_1,t_2) = \sum_{j \geq 0} \ch_{SU(3)}^{\lambda_3+j} (t_1^{-1},t_2^{-1}) x^j .
\eeqn
where we recall that $\ch_{SU(3)}^{\lambda_3+j} (t_1,t_2)$ is the $SU(3)$ character of the irreducible $SU(3)$ representation of highest weight $(\lambda_1+j,0)$. 
It will be convenient to define the polynomial 
\beqn\label{eqn:h1}
h_{\lambda_1}(t_1,t_2,x) = t_2 (t_1^{-1} t_2 - x) \left(1 + t_1^{-1} t_2^2 + \cdots + t_1^{-\lambda_1+1} t_2^{2 \lambda_2 -2}\right)  .
\eeqn

\begin{lem}
One has
\beqn
\til p_{\lambda_1} (x,t_1,t_2) = \frac{p_{\lambda_1}(x,t_1,t_2)}{(1-t_1^{-1} x)(1-t_1t_2^{-1} x)(1-t_2 x)} .
\eeqn
where the polynomial $p_{\lambda_1}(x,t_1,t_2)$ is given by
\beqn
p_{\lambda_1}(x,t_1,t_2) = 1 + (1+t_1 t_2 - t_2 x) h(t_1,t_2,x)
\eeqn 
\end{lem} 
\begin{proof}
\begin{multline}
t_1^{\lambda_1} t_2^{-\lambda_1} \sum_{j \geq 0} t_1^{j} t_2^{-j} x^j \sum_{k=0}^{\lambda_1 + j}t_1^{-k} t_2^{2k} \frac{1 - t_1^{-k-1} t_2^{-k-1}}{1-t_1^{-1} t_2^{-1}}  \\
= \frac{t_1^{\lambda_1} t_2^{-\lambda_1}}{1-t_1^{-1} t_2^{-1}} \sum_{j \geq 0} \sum_{k=0}^{\lambda_1 + j} t_1^{j-k} t_2^{-j+2k} x^j \left(1 - t_1^{-k-1} t_2^{-k-1}\right) \\ 
= \frac{t_1^{\lambda_1} t_2^{-\lambda_1}}{1-t_1^{-1} t_2^{-1}} \sum_{j \geq 0} \left(t_1^j t_2^{-j} \frac{1-(t_1^{-1} t_2^{2})^{\lambda_1+j+1}}{1-t_1^{-1} t_2^{2}} - t_1^{j-1} t_2^{-j-1} \frac{1 - (t_1^{-2} t_2)^{\lambda_1+j+1}}{1 - t_1^{-2} t_2} \right) x^j  \\
%= \frac{t_1^{\lambda_1} t_2^{-\lambda_1}}{(1-t_1^{-1} t_2^{2})} \sum_{j \geq 0} \left( t_1^j t_2^{-j} (1-(t_1^{-1} t_2^{2})^{\lambda_1+j+1})(1 - t_1^{-2} t_2) \right. \\ \left. - t_1^{j-1} t_2^{-j-1} (1 - (t_1^{-2} t_2)^{\lambda_1+j+1})(1-t_1^{-1} t_2^{2}) \right) x^j \\ 
= F(t_1,t_2) \left( G_1 (t_1,t_2,x) - t_1^{-1} t_2^{-1} G_2 (t_1,t_2,x)\right) .
\end{multline}

@@

Write $G_1 = g_1 / (1- t_1^{-1} t_2^2)$ and consider the polynomial
\beqn
\label{eqn:h2}
 (1-t_2 x)(1-t_1 t_2^{-1} x) g_1(t_1,t_2,x)
= 1 - t_1^{-\lambda_1} t_2^{2 \lambda_1 + 1} - t_2 x + t_1^{-\lambda_1} t_2^{2 \lambda_1 + 1} x .
\eeqn
This polynomial is clearly divisible by $1-t_1^{-1} t_2^2$ so we can define the polynomial
\beqn
\til h_{\lambda_1}(t_1,t_2,x) = \frac{(1-t_2 x)(1-t_1 t_2^{-1} x) g_1(t_1,t_2,x)}{1-t_1^{-1} t_2^2} 
\eeqn
By definition we have
\beqn
G_1(t_1,t_2,x) = \frac{\til h (t_1, t_2,x)}{(1-t_2 x)(1-t_1 t_2^{-1} x)} .
\eeqn

@@

From this lemma we conclude that
\beqn
\til{p}_{\lambda_1}(t_1,t_2,x) = \frac{t_1^{\lambda_1} t_2^{-\lambda_1}}{{(1-t_1^{-1} x)(1-t_1t_2^{-1} x)(1-t_2 x)}} \left(1 + (1+t_1 t_2 - t_2 x) h(t_1,t_2,x)\right)
\eeqn
and the result follows.
\end{proof}

>>>>

The first ingredient in determining an explicit formula for Verma modules is a direct calculation.
\begin{lem}
\label{lem:R}
The explicit formula for $R = R(t,t_1,t_2,r)$ is
%\beqn
%R = \frac{1}{(1-t_1^{-1} q)(1-t_1t_2^{-1}q)(1-t_2 q)}\prod_{a=+1,-1}(1-t_1^{-1} q^{1/2} r^a)(1-t_1 t_2^{-1} q^{1/2} r^a)(1-t_2 q^{1/2} r^a)
%\eeqn
\beqn
R = \frac{1}{(1-t_1^{-1} q)(1-t_1t_2^{-1}q)(1-t_2 q)}\prod_{a=+1,-1}(1-t_1 q^{1/2} r^a)(1-t_1^{-1} t_2 q^{1/2} r^a)(1-t_2^{-1} q^{1/2} r^a)
\eeqn
\end{lem}

@@

%\parsec[s:unrefinedA]
%
%In this section we deduce an explicit formula for the character of the type $A$ modules $I_A(\lambda_1,\lambda_3)$ after specializing $t_1=t_2=1$. 
%
%\begin{prop}
%\label{prop:chA}
%Let $\lambda_1,\lambda_3 \geq 0$. 
%The $t_1=t_2=1$ specialization of $\ch \, \til I_A(\lambda_1,\lambda_3)$ is given by the expression
%\beqn
%\frac{t^{2\lambda_1-3 \lambda_3+6}}{(1-t^2)^3(1-r^{-2})} \left(r^{\lambda_3} p_{\lambda_1}(t^{-1}r) (1-t^{-1}r^{-1})^3 - r^{-\lambda_3-2} p_{\lambda_1}(t^{-1}r^{-1})(1-t^{-1}r)^3 \right) 
%\eeqn
%where $p_{\lambda_1}(x) = \frac12 \left(\lambda_1^2 x^2 + \lambda_1 x^2 - 2\lambda_1^2x -4 \lambda_1 x + \lambda_1^2 + 3\lambda_1 +2\right)$. 
%\end{prop}
%
%\begin{proof}
%In this specialization we just see the dimension of the highest weight $SU(3)$ representations
%\[
%\ch_{SU(3)}^{\lambda_1+j}(t_1=t_2=1) = \frac{(\lambda_1+j+1)(\lambda_1+j+2)}{2} .
%\]
%
%We thus arrive at the expression for the $j$th term in the sum appearing in equation \eqref{eqn:chA2}:
%\beqn\label{eqn:MA2}
%\ch \til M_A(\lambda_1+j,\lambda_3+j)_{t_1=t_2=1} = R(t,r) t^{2 \lambda_1-3\lambda_3-j} \frac{(\lambda_1+j+1)(\lambda_1+j+2)}{2} \frac{r^{\lambda_3+j}-r^{-\lambda_3-j-2}}{1-r^{-2}} 
%\eeqn
%where $R(t,r)$ is the specialization at $t_1=t_2=1$ of $R$ from Lemma \ref{lem:R}:
%\[
%R(t,r) = R|_{t_1=t_2=1} = \frac{(1-tr)^3 (1-t r^{-1})^3}{(1-t^2)^3} .
%\]
%In equation \eqref{eqn:MA2} we have also utilized the $SU(2)$ character formula for the irreducible module of heighest weight $\lambda_3+j$. 
%%\[
%%r^{\lambda_3+j}+ r^{\lambda_3+j-2} + \cdots + r^{-\lambda_3-j} = \frac{r^{\lambda_3+j}-r^{-\lambda_3-j-2}}{1-r^{-2}} ,
%%\]
%
%Now, observe the formal identity 
%\[
%\sum_{j \geq 0} \frac{(\lambda_1+j+1)(\lambda_1+j+2)}{2} x^j = \frac{p_{\lambda_1}(x)}{(1-x)^3}  
%\]
%where $p_{\lambda_1}(x)$ is as in the statement of the proposition.
%Using this identity, we evaluate
%\begin{align*}
%\ch \til I_A(\lambda_1,\lambda_3)|_{t_1=t_2=1} & = \frac{R(r,t) t^{2 \lambda_1-3 \lambda_3}}{1-r^{-2}} \left(\frac{r^{\lambda_3} p_{\lambda_1}(t^{-1}r)}{(1-t^{-1}r)^3} - \frac{r^{-\lambda_3-2}p_{\lambda_1}(t^{-1}r^{-1})}{(1-t^{-1}r^{-1})^3} \right) \\ 
%& = \frac{t^{2\lambda_1-3 \lambda_3+6}}{(1-t^2)^3(1-r^{-2})} \left(r^{\lambda_3} p_{\lambda_1}(t^{-1}r) (1-t^{-1}r^{-1})^3 \right. \\ & \left. - r^{-\lambda_3-2} p_{\lambda_1}(t^{-1}r^{-1})(1-t^{-1}r)^3 \right) .
%\end{align*}
%This completes the proof
%\end{proof}
%
%In the case that $\lambda_1=0$ and $\lambda_3=1$ we see that this specialized character simplifies to
%\beqn
%\ch \til I_A(0,1)|_{t_1=t_2=1} = \frac{t^3(r+r^{-1}) + 1 - 3 t^2}{(1-t^2)^3} .
%\eeqn
%
%In the case that $\lambda_1 = 1$ and $\lambda_3 = 0$ we see that this unrefined character simplifies to
%\beqn
% \ch \til I_A(1,0)|_{t_1=t_2=1} = \frac{t^6(r^2 + r^{-2} + 1) - 3 t^7 (r + r^{-1}) + 3t^8 }{(1-t^2)^3} .
%\eeqn
%
%Finally, for general $\lambda_1,\lambda_3$ we specialize further $t=r$ and substitute $q = t^2$ to obtain
%\beqn
%\ch \til I_A(\lambda_1,\lambda_3) = \frac{t^{2 \lambda_1 - 2 \lambda_3 + 2}}{1 - t^2} = \frac{q^{\lambda_1-\lambda_3+1}}{1-q} .
%\eeqn

@@

We now turn to the formula for the totally unrefined character of $\til I_A(\lambda_1,\lambda_3)$ as a function of the fugacities $t,t_1,t_2,r$.
To state the result we introduce some notation.

For $\lambda_1 \geq 0$ define the polynomial in the variables $t_i^{\pm 1}$ and an auxiliary variable $x$
\beqn\label{eqn:p}
p_{\lambda_1}(t_1,t_2,x) = t_1^{\lambda_1} t_2^{-\lambda_1} \left(1 + (1+t_1^{-1} t_2^{-1} - t_1^{-1} x) h(t_1,t_2,x)\right) 
\eeqn
where for $\lambda_1 > 0$
\beqn\label{eqn:h1}
h_{\lambda_1}(t_1,t_2,x) = t_2 (t_1^{-1} t_2 - x) \left(1 + t_1^{-1} t_2^2 + \cdots + t_1^{-\lambda_1+1} t_2^{2 \lambda_2 -2}\right)  
\eeqn
and for $\lambda_1 = 0$ we set $h_0 (t_1,t_2,x) = 0$.

Our main result of this section is the following.
\begin{thm}
\label{thm:refinedA}
For any $\lambda_1,\lambda_3 \geq 0$ the character of $\til I_A(\lambda_1,\lambda_3)$ is given by the following expression
\begin{multline}
\frac{t^{2 \lambda_1 - 3 \lambda_3+6}}{(1-t_1^{-1} t^2)(1-t_1t_2^{-1}t^2)(1-t_2 t^2)(1-r^{-2})} \times \\
\left(r^{\lambda_3} p_{\lambda_1}(t_1,t_2,t^{-1} r) (1-t_1^{-1} r^{-1} t^{-1})(1-t_1t_2^{-1} r^{-1} t^{-1})(1-t_2 r^{-1} t^{-1}) \right.
\\
- \left. r^{-\lambda_3 - 2} p_{\lambda_1}(t_1,t_2,r^{-1} t^{-1})(1-t_1^{-1} r t^{-1})(1-t_1t_2^{-1} r t^{-1})(1-t_2 r t^{-1}) \right)
\end{multline}
\end{thm}

Recall that the character is given by the infinite sum
\beqn
\ch \til I_A (\lambda_1,\lambda_3) = \sum_{j \geq 0} \ch \til M_A(\lambda_1+j, \lambda_3+j)
\eeqn
For each $j \geq 0$ we have
\begin{multline}
\ch \til M_A(\lambda_1+j, \lambda_3+j) = R \cdot t^{2 \lambda_1-3 \lambda_3-j} \cdot \ch_{SU(3)}^{\lambda_1+j} \cdot \ch^{\lambda_3+j}_{SU(2)} \\ =
\frac{t^{2 \lambda_1 - 3 \lambda_3} R}{1-r^{-2}} \ch_{SU(3)}^{\lambda_1+j} t^{-j} (r^{\lambda_3 + j} - r^{-\lambda_3 - j - 2}).
\end{multline}

The first step is to deduce a closed formula for the following generating function
\beqn
\til p^{\lambda_1} (x,t_1,t_2) = \sum_{j \geq 0} \ch_{SU(3)}^{\lambda_3+j} (t_1^{-1},t_2^{-1}) x^j .
\eeqn
where we recall that $\ch_{SU(3)}^{\lambda_3+j} (t_1,t_2)$ is the $SU(3)$ character of the irreducible $SU(3)$ representation of highest weight $(\lambda_1+j,0)$.

\begin{lem}
\label{lem:generating}
One has
\beqn
\til p_{\lambda_1} (t_1,t_2,x) = \frac{p_{\lambda_1}(t_1,t_2,x)}{(1-t_1^{-1} x)(1-t_1t_2^{-1} x)(1-t_2 x)} .
\eeqn
where the polynomial $p_{\lambda_1}(x,t_1,t_2)$ is given by equation \eqref{eqn:p}.

\end{lem} 
\begin{proof}
\begin{multline}
t_1^{\lambda_1} t_2^{-\lambda_1} \sum_{j \geq 0} t_1^{j} t_2^{-j} x^j \sum_{k=0}^{\lambda_1 + j}t_1^{-k} t_2^{2k} \frac{1 - t_1^{-k-1} t_2^{-k-1}}{1-t_1^{-1} t_2^{-1}}  \\
= \frac{t_1^{\lambda_1} t_2^{-\lambda_1}}{1-t_1^{-1} t_2^{-1}} \sum_{j \geq 0} \sum_{k=0}^{\lambda_1 + j} t_1^{j-k} t_2^{-j+2k} x^j \left(1 - t_1^{-k-1} t_2^{-k-1}\right) \\ 
= \frac{t_1^{\lambda_1} t_2^{-\lambda_1}}{1-t_1^{-1} t_2^{-1}} \sum_{j \geq 0} \left(t_1^j t_2^{-j} \frac{1-(t_1^{-1} t_2^{2})^{\lambda_1+j+1}}{1-t_1^{-1} t_2^{2}} - t_1^{j-1} t_2^{-j-1} \frac{1 - (t_1^{-2} t_2)^{\lambda_1+j+1}}{1 - t_1^{-2} t_2} \right) x^j  \\
%= \frac{t_1^{\lambda_1} t_2^{-\lambda_1}}{(1-t_1^{-1} t_2^{2})} \sum_{j \geq 0} \left( t_1^j t_2^{-j} (1-(t_1^{-1} t_2^{2})^{\lambda_1+j+1})(1 - t_1^{-2} t_2) \right. \\ \left. - t_1^{j-1} t_2^{-j-1} (1 - (t_1^{-2} t_2)^{\lambda_1+j+1})(1-t_1^{-1} t_2^{2}) \right) x^j \\ 
= F(t_1,t_2) \left( G_1 (t_1,t_2,x) - t_1^{-1} t_2^{-1} G_2 (t_1,t_2,x)\right) .
\end{multline}

@@

Write $G_1 = g_1 / (1- t_1^{-1} t_2^2)$ and consider the polynomial
\beqn
\label{eqn:h2}
 (1-t_2 x)(1-t_1 t_2^{-1} x) g_1(t_1,t_2,x)
= 1 - t_1^{-\lambda_1-1} t_2^{2 \lambda_1 + 2} - t_2 x + t_1^{-\lambda_1} t_2^{2 \lambda_1 + 1} x .
\eeqn
This polynomial is clearly divisible by $1-t_1^{-1} t_2^2$ so we can define the polynomial
\beqn
\til h_{\lambda_1}(t_1,t_2,x) = \frac{(1-t_2 x)(1-t_1 t_2^{-1} x) g_1(t_1,t_2,x)}{1-t_1^{-1} t_2^2} 
\eeqn
By definition we have
\beqn
G_1(t_1,t_2,x) = \frac{\til h (t_1, t_2,x)}{(1-t_2 x)(1-t_1 t_2^{-1} x)} .
\eeqn

@@

From this intermediate lemma we conclude that
\beqn
\til{p}_{\lambda_1}(t_1,t_2,x) = \frac{t_1^{\lambda_1} t_2^{-\lambda_1}}{{(1-t_1^{-1} x)(1-t_1t_2^{-1} x)(1-t_2 x)}} \left(1 + (1 +t_1^{-1}t_2^{-1}- t_1^{-1} x) h(t_1,t_2,x)\right)
\eeqn
Which completes the proof of Lemma \ref{lem:generating}. 
\end{proof}

Now, the proof of Theorem \ref{thm:refinedA} is an immediate computation. 
\begin{multline}
\ch \til I_A(\lambda_1,\lambda_2) = \frac{t^{2 \lambda_1 - 3 \lambda_3} R}{1-r^{-2}} \left(r^{\lambda_3} \frac{p_{\lambda_1}(t_1,t_2,r t^{-1})}{(1-t_1^{-1} r t^{-1})(1-t_1t_2^{-1} r t^{-1})(1-t_2 r t^{-1})}  \right. \\ \left. - r^{-\lambda_3-2} \frac{p_{\lambda_1}(t_1,t_2,r^{-1} t^{-1})}{(1-t_1^{-1} r^{-1} t^{-1})(1-t_1t_2^{-1} r^{-1} t^{-1})(1-t_2 r^{-1} t^{-1})}\right) \\  
= \frac{t^{2 \lambda_1 - 3 \lambda_3+6}}{(1-t_1^{-1} t^2)(1-t_1t_2^{-1}t^2)(1-t_2 t^2)(1-r^{-2})} \times \\
\left(r^{\lambda_3} p_{\lambda_1}(t_1,t_2,t^{-1} r) (1-t_1^{-1} r^{-1} t^{-1})(1-t_1t_2^{-1} r^{-1} t^{-1})(1-t_2 r^{-1} t^{-1}) \right.
\\
- \left. r^{-\lambda_3 - 2} p_{\lambda_1}(t_1,t_2,r^{-1} t^{-1})(1-t_1^{-1} r t^{-1})(1-t_1t_2^{-1} r t^{-1})(1-t_2 r t^{-1}) \right) .
\end{multline}

\parsec[s:tests]

We can greatly simplify expressions for the character of $\til I_A(\lambda_1,\lambda_3)$ for small values of $\lambda_1,\lambda_3$. 
The following corollaries are immediate computations.

\begin{cor} 
\label{cor:6dtest1}
When $(\lambda_1,\lambda_3) = (0,1)$ one has 
\beqn\label{eqn:6doneTest}
\ch \til I_A(0,1) = \frac{(r + r^{-1})t^{3} - (t_1 + t_1^{-1} t_2 + t_2^{-1} )t^4 + t^6}{(1-t_1^{-1}t^2) (1-t_1 t_2^{-1} t^2) (1-t_2 t^2)} .
\eeqn
\end{cor}

Note that upon substituting $q = t^2$ this agrees with the our direct computation of the character of local operators on the holomorphic twist of the six-dimensional theory abelian superconformal theory from Proposition \ref{prop:6done}.

The next easy case is the following.
\begin{cor}
\label{cor:6dtest2}
When $(\lambda_1,\lambda_3) = (1,0)$ one has  
\beqn\label{eqn:6dtwo}
\ch \til I_A(1,0) = \frac{t^8(t_1^{-1} + t_1 t_2^{-1}  + t_2) + t^6 (r^2 + r^{-2} + 1) - t^{7} (r + r^{-1})(t_1 + t_1^{-1} t_2 + t_2^{-1})}{(1-t_1^{-1}t^2) (1-t_1 t_2^{-1} t^2) (1-t_2 t^2)} .
\eeqn
\end{cor}

Again, we note that upon substituting $q = t^2$ this agrees with the our direct computation of the character of local operators on the holomorphic twist of our conjectural description of the six-dimensional superconformal theory associated to the Lie algebra $\lie{sl}(2)$ which we computed in Proposition \ref{prop:6dtwo}.

### 2022-07-21 fivebranes/ops.tex
allinone
merge

\begin{prop}
The character $\chi_{u(1)}(q,t_1,t_2,r)$ of local operators of the holomorphic twist of the theory on a single fivebrane is given by the plethystic exponential of the single particle index
\[
f^{6d}_{u(1)} (q,t_1,t_2,r) = \frac{(r + r^{-1})q^{3/2} - (t_1 + t_1^{-1} t_2 + t_2^{-1} )q^2 + q^3}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)} .
\]
\end{prop}

@@

\begin{itemize}
\item Single particle operators coming from the copy of holomorphic vector fields $\Vect^{hol}(\C^3)$ contribute
\[
q^3 \frac{t_1^{-1} q + t_1 t_2^{-1} q + t_2 q }{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)} 
\]
\item Single particle operators coming from $\lie{sl}(2)$-valued holomorphic functions $\lie{sl}(2) \otimes \cO^{hol}(\C^3)$ contribute
\[
q^3\frac{r^2 + r^{-2} + 1}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)} 
\]
\item Single particle operators coming from the odd piece of $E(3|6)$ which is $\Omega^{1,hol} \otimes K^{-1/2} \otimes \C^2$ contribute
\[
q^{3}\frac{(q^{1/2} r + q^{1/2} r^{-1})(t_1^{-1} + t_1t_2^{-1} + t_2)}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)}
\]
\end{itemize}

\begin{conj}
The character of local operators of the holomorphic twist of the theory on a stack of two fivebranes is given by the following plethystic exponential
\[
\chi_{\lie{sl}(2)}^{6d} (q,t_1,t_2,r) = {\rm PExp} \left[f_{\lie{sl}(2)}^{6d} (t_1,t_2,q,r) \right] .
\]
where the single particle index is
\[
f_{\lie{sl}(2)}^{6d} (q, t_1,t_2,r) = \frac{q^4(t_1^{-1} + t_1 t_2^{-1}  + t_2) + q^3 (r^2 + r^{-2} + 1) - q^{7/2} (r + r^{-1})(t_1^{-1} + t_1t_2^{-1} + t_2)}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)} .
\]
\end{conj}

>>>>

\begin{prop}
\label{prop:6done}
The character $\chi_{u(1)}(q,t_1,t_2,r)$ of local operators of the holomorphic twist of the theory on a single fivebrane is given by the plethystic exponential of the single particle index
\beqn\label{eqn:6done}
f^{6d}_{u(1)} (q,t_1,t_2,r) = \frac{(r + r^{-1})q^{3/2} - (t_1 + t_1^{-1} t_2 + t_2^{-1} )q^2 + q^3}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)} .
\eeqn
\end{prop}

@@

\begin{itemize}
\item Single particle operators coming from the copy of holomorphic vector fields $\Vect^{hol}(\C^3)$ contribute
\[
q^3 \frac{t_1^{-1} q + t_1 t_2^{-1} q + t_2 q }{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)} 
\]
\item Single particle operators coming from $\lie{sl}(2)$-valued holomorphic functions $\lie{sl}(2) \otimes \cO^{hol}(\C^3)$ contribute
\[
q^3\frac{r^2 + r^{-2} + 1}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)} 
\]
\item Single particle operators coming from the odd piece of $E(3|6)$ which is $\Omega^{1,hol} \otimes K^{-1/2} \otimes \C^2$ contribute
\[
q^{3}\frac{(q^{1/2} r + q^{1/2} r^{-1})(t_1 + t_1^{-1} t_2 + t_2^{-1})}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)}
\]
\end{itemize}

Combining these expressions we obtain the following.

\begin{prop} \label{prop:6dtwo}
The character of local operators of the factorization algebra $\clie_\bu(\cG_{2,c})$ on $\C^3$ is given by the following expression
\beqn\label{eqn:6dtwo1}
\frac{q^4(t_1^{-1} + t_1 t_2^{-1}  + t_2) + q^3 (r^2 + r^{-2} + 1) - q^{7/2} (r + r^{-1})(t_1 + t_1^{-1} t_2 + t_2^{-1})}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)} .
\eeqn
\end{prop}

Based on our discussion above we are led to the following conjecture.
\begin{conj}\label{conj:6dtwo}
The character of local operators of the holomorphic twist of the theory on a stack of two fivebranes is given by the following plethystic exponential
\[
\chi_{\lie{sl}(2)}^{6d} (q,t_1,t_2,r) = {\rm PExp} \left[f_{\lie{sl}(2)}^{6d} (t_1,t_2,q,r) \right] .
\]
where the single particle index is
\beqn\label{eqn:6dtwo}
f_{\lie{sl}(2)}^{6d} (q, t_1,t_2,r) = \frac{q^4(t_1^{-1} + t_1 t_2^{-1}  + t_2) + q^3 (r^2 + r^{-2} + 1) - q^{7/2} (r + r^{-1})(t_1 + t_1^{-1} t_2 + t_2^{-1})}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)} .
\eeqn
\end{conj}
